---
title: "Assignment 1 - Information Management"
author: "Niha Yadav"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-summary: "Show R Code"
---


## **🔗 Navigation**
-  [Question 1](#question1)  
-  [Question 2](#question2)  
-  [Question 3](#question3)  
-  [Question 6](#question6)  

---

## **Question 1: University Systems** {#question1}

### **University System (Student Information System)**  
**Purpose:** Manages and maintains student information.  
**Functions:**  
- Course Registration  
- Academic Records  
- Personal Information  
- Financial Information  
Example: UT Dallas uses Oracle PeopleSoft Campus Solutions 

### **Online Learning Platform (Learning Management System)**  
**Purpose:** Facilitates electronic learning and communication.  
**Functions:**  
- Courses  
- Grades  
- Calendar  
- Communication  
Example: UT Dallas uses Blackboard's e-learning  

### **Online Banking System (Financial System)**  
**Purpose:** Offers financial management and access to banking systems.  
**Functions:**  
- Money Transfer  
- Security  
- Mobile Banking  
- Account Management  
Example: Bank of America Online Banking  

---

## **Question 2: Data-Driven Platforms** {#question2}

### **Criminology: Crime Data Analysis Platform**  
**Purpose:** Analyze and visualize crime data, helping law enforcement agencies identify crime patterns and improve public safety.  
**Functions:**  
  Data Visualization (heatmaps, trends).  
  Predictive Analytics (future crime occurrences).  
  Reporting (crime statistics reports).  
  Collaboration (data sharing, inter-agency tools).  

**Simple Interface Design:**  
- Dashboard: Key crime metrics, maps, trend charts.  
- Analysis Tools: Filtering data by crime type, location, and time.  
- Reports: Generate and export reports.  
- Collaboration: Chat and document sharing.  

---

### **Brain Science: Cognitive Training App**  
**Purpose:** Provide cognitive training exercises and assessments to track cognitive health.  
**Functions:**  
  Training Programs (memory, problem-solving).  
  Progress Tracking (performance feedback).  
  Assessments (evaluate brain function).  
  Reminders (daily training sessions).  

**Simple Interface Design:**  
- Home Screen: Dashboard with progress charts.  
- Training Exercises: Personalized cognitive tasks.  
- Assessments: Cognitive evaluations and reports.  
- Reminders: Notifications for training sessions.  

---

### **Economics: Personal Finance Management App**  
**Purpose:** Help individuals manage personal finances, track expenses, and plan future goals.  
**Functions:**  
  Budgeting (set budgets, track spending).  
  Financial Goals (saving, debt payoff).  
  Expense Categorization (spending patterns).  
  Reports (financial visualizations).  

**Simple Interface Design:**  
- Home Screen: Budget status, spending summary.  
- Expense Tracker: Add and categorize expenses.  
- Financial Goals: Set and monitor savings progress.  
- Reports: Charts to visualize financial health.  

---

## **Question 3: Importance of Data Mining** {#question3}

**Why is data mining necessary?**  
✔ Discovering hidden patterns in data.  
✔ Predicting future trends.  
✔ Improving decision-making.  
✔ Enhancing efficiency.  
✔ Personalizing user experiences.  

---

## **Question 6: Example Tables (Users, Posts, Comments)** {#question6}

Below are three database tables used in a typical social media system:  

```{r}
# Users table
users_table <- data.frame(
  user_id = 1:5,
  username = c("john_doe", "alice_wonder", "bob_smith", "carol_jones", "eve_wood"),
  email = c("john@example.com", "alice@example.com", "bob@example.com", "carol@example.com", "eve@example.com"),
  created_at = Sys.time() - sample(1:1000, 5),
  updated_at = Sys.time()
)
# Display the table
users_table
```


```{r}
# Posts table
posts_table <- data.frame(
  post_id = 1:5,
  user_id = c(1, 2, 1, 3, 4),
  content = c("First post", "Second post", "Another post", "Interesting post", "Final post"),
  created_at = Sys.time() - sample(1:1000, 5),
  updated_at = Sys.time(),
  likes_count = c(10, 5, 8, 2, 7),
  comments_count = c(2, 1, 4, 0, 3),
  shared_count = c(3, 1, 2, 0, 1)
)
# Display the table
posts_table
```


```{r}
# Comments table
comments_table <- data.frame(
  comment_id = 1:5,
  post_id = c(1, 1, 2, 3, 4),
  user_id = c(2, 3, 1, 4, 5),
  content = c("Great post!", "Interesting!", "Thanks for sharing!", "Nice!", "I agree!"),
  created_at = Sys.time() - sample(1:1000, 5),
  updated_at = Sys.time(),
  likes_count = c(5, 2, 3, 1, 4)
)
# Display the table
comments_table
```